Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-07-09 manuscript/manuscript_pve.Rmd
cleaned plotting scripts
deleted model table as we no longer use it
new cue figure, not in folder yet
new results from modelled C gain and CUE

bolded discussion for remko to look at, probably need to delete

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

source("manuscri[t/manuscript_preload.R")

@@

\
It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling leaf *A*~n~ with total plant leaf area. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma et al. [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*. All default parameters used in model simulations are reported in Table `r pvetabS`.

*make sure this is correct, add CUE bit*
We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.  Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.

@@

##Whole-plant C balance
*this needs to reflect C gain vs mass*
Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %. Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 11&pm;2.3 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 45&pm;6.2 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.

@@

##Do reductions in photosynthesis explain reductions in seedling growth?
Our model used a simple approach to drive seedling growth with measured reductions in leaf *A*~n~ , via soil volume effects, while treating C use efficiency, respiration and C allocation as fixed processes. Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings. Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al. [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth. These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation]. It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely. Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant. Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven plant growth models [@lacointe2000carbon].

\
Focusing only on empirical results in this study points to *A*~n~ driving reductions in seedling growth. Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation. This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant carbon balance can lead to erroneous conclusions [@valentini2000respiration]. For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models. The use of fixed rates of respiration in our model likely underestimates seedling responses to sink limitation. Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents. Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves. However, the degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

source("manuscript/manuscript_preload.R")

@@

\
It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling leaf *A*~n~ with total plant leaf area. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma et al. [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*.

\
We used the model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.  Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings. We then compared seedling carbon use efficiency (CUE) across treatments, as the proportion of modelled cumulative net leaf C gain allocated to observed seedling biomass.

@@

##Whole-plant C balance
Modelled cumulative net leaf C gain over 120 days varied two-fold across containers sizes (25.6 - 55.1 g C). The free seedling control had five-fold greater modelled total C gain than the average of container treatments (213.6 - 42.7&pm;8.2 g C). For seedlings in containers, an average of 67 &pm;0.01 % of modelled C gain was not allocated to biomass, compared to 59.2 % for the free seedling control (Figure `r massmodelfig`a). Consequently, the average CUE of containerized seedlings (32&pm;0.01 %) was lower than the free seedling control (40.8 %) (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A*~n~ with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.

@@

##Do reductions in photosynthesis explain reductions in seedling growth?
Our model used a simple approach to estimate cumulative seedling C gain with measured reductions in leaf *A*~n~ , via soil volume effects. *while treating C use efficiency, respiration and C allocation as fixed processes*. *Contrary to expectation, the model consistently overestimated seedling growth in containers when parameterized with an optimized LMF for free seedlings.* Although reductions in both *A*~max~ and biomass were strongly correlated among treatments, as hypothesized by Poorter et al. [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth. These findings are important as this model reflects classical approaches in tree growth and production modelling that are driven by inputs of C assimilation and *processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation].* It is possible that the overestimation of growth was due to an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *Vc*~max~, *R*~dark~ and *g*~1~) make this unlikely. Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant. Doing so will provide valuable input to future models as assimilate allocation is a key component in carbon-balance driven plant growth models [@lacointe2000carbon].

\
Focusing only on empirical results in this study points to *A*~n~ driving reductions in seedling growth. Our modelling results reveal that other components of the C balance, beyond *A*~n~, are required to explain the observed seedling biomass response to sink manipulation. This discrepancy is noteworthy, as partial accounting of the different mechanisms involved in plant C balance can lead to erroneous conclusions [@valentini2000respiration].*For example, the fraction of photosynthate used in respiration is known to vary depending on species and local environmental conditions [@Lambers2008], yet is often considered a static parameter in process based growth models. The use of fixed rates of tissue respiration in our model likely underestimates seedling responses to sink limitation.* Thus, our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents. Future empirical and modelling studies should focus on how feedbacks from sink activity affect both rates of *A*~n~ and the fate of C allocated to growth, respiration and C storage in leaves. However, the degree to which these mechanisms regulate the C available for growth will undoubtedly shift across different species and environmental conditions.
